### 2022-12-08 chapter1/chapter1_supporting.tex
Updated caption for hmm_trim figure

\begin{figure}[h!]
\includegraphics[width=\textwidth]{hmm_trim/out/hmm_trim.png}
\centering
\caption{\textbf{Insertion phylo-HMM trimming details.}
\textbf{(A)} Most alignments were not trimmed of any columns. \textbf{(B)} Most alignments have fewer than 5 trimmed regions which cumulatively account for less than 10\% of the columns in the original alignment. Alignments with more trimmed columns generally have one one large trimmed region rather than many small ones. \textbf{(C)} Most trimmed regions were inferred as state 3.}
\label{sfig:hmm_trim}
\end{figure}

>>>>

\begin{figure}[h!]
\includegraphics[width=\textwidth]{hmm_trim/out/hmm_trim.png}
\centering
\caption{\textbf{Insertion phylo-HMM trimming details.}
\textbf{(A)} Most alignments were not trimmed. Of the alignments with trims, most were trimmed only at the level of sequences. \textbf{(B)} Most trimmed regions were inferred primarily as state 2. \textbf{(C)} Most alignments with sequence trims have fewer than 10 segments removed. \textbf{(D)} Most alignments with region trims have fewer than five regions removed. \textbf{(E, G)} The number of non-gap symbols in sequence trims can vary considerably, but for nearly all sequence trims each non-gap symbol in the removed segment is aligned to fewer than five non-gap symbols on average. \textbf{(F, H)} The length of region trims can also vary considerably, but generally each region trims accounts for fewer than 10\% of the columns in the original alignment.}
\label{sfig:hmm_trim}
\end{figure}
